\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-01-10 presentations/popl19-01-2019/presentation.tex
Update presentation

\usepackage{xcolor}
\input{preamble}

@@

\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{calc}
\usepackage{graphicx}
\usepackage{dashrule}

@@

\begin{frame}[fragile]
  \frametitle{Defining well-bracketed control flow and local state encapsulation}
  \begin{columns}
    \begin{column}{0.5\textwidth}
\begin{lstlisting}[language=C, escapechar=!]
void a()       !\tikz[remember picture] \node[] (bt) {};! 
{
  !\tikz[remember picture] \node[] (pc6) {};!...
  !\tikz[remember picture] \node[] (pc7) {};!return;      
}              !\tikz[remember picture] \node[] (bb) {};!

void b()
{
  !\tikz[remember picture] \node[] (pc1) {};!int x = 5;
  !\tikz[remember picture] \node[] (pc2) {};!a();
  !\tikz[remember picture] \node[] (pc3) {};!...
  !\tikz[remember picture] \node[] (pc4) {};!a();
  !\tikz[remember picture] \node[] (pc5) {};!return;   
}
\end{lstlisting}
      \begin{tikzpicture}[remember picture, overlay, text width=3cm]
%        \draw<1> node { };
        \draw<2>[decorate,decoration={brace,amplitude=6pt,raise=4pt},yshift=0pt] ($(bt) + (0,0.2)$) -- ($(bb) + (0,-0.2)$) node[xshift=-1cm] (brace) [midway] {};
        \draw<2> node[right = -0cm of brace] {Function \texttt{a} cannot access variable \texttt{x}};

        \draw<3-> ($(pc1) + (-0.5,0)$) edge[-stealth] node {} (pc1);
      \end{tikzpicture}
    \end{column}
    \begin{column}{0.5\textwidth}
      \only<2>{Local-state encapsulation}
      \only<3->{Well-bracketed control flow}
    \end{column}
    % What is LSE and WBCF
    % Quick example?
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{Fully-abstract overlay semantics}
  \centering
  \begin{tikzpicture}
    \draw (0,0) node[draw=black, rounded corners] (olcm) {oLCM};
    \draw node[draw=black, rounded corners,below=2.5cm of olcm] (lcm) {LCM};
    \draw (olcm) edge[bend left, ->,thick] (lcm);
    \draw node[left = 3cm of olcm] (ll1) {};
    \draw node[right = 3cm of olcm] (rl1) {};
    \draw node[below = 1.25cm of ll1] (ll) {};
    \draw node[below = 1.25cm of rl1] (rl) {};
    \draw[dashed] (ll) -- (rl);

    \draw<1> (olcm) edge[bend left, ->,thick] node[right, near start] { } (lcm);
    \draw<2-> (olcm) edge[bend left, ->,thick] node[right, near start] {$id$} (lcm);
  \end{tikzpicture}
\end{frame}

@@

>>>>

\usepackage{appendixnumberbeamer}
\usepackage{xcolor}
\input{preamble}

@@

\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{calc}
\usetikzlibrary{arrows,shapes}
\usepackage{graphicx}
\usepackage{dashrule}

@@

\begin{frame}[fragile]
  \frametitle{Defining well-bracketed control flow and local state encapsulation}
  \begin{columns}
    \begin{column}{0.5\textwidth}
\begin{lstlisting}[language=C, escapechar=!]
!\tikz[remember picture] \node[] (a) {};!void a()       !\tikz[remember picture] \node[] (bt) {};! 
{
  !\tikz[remember picture] \node[] (pc6) {};!...
  !\tikz[remember picture] \node[] (pc7) {};!return;!\tikz[remember picture] \node[] (ret) {};!      
}               !\tikz[remember picture] \node[] (bb) {};!

void b()
{
  !\tikz[remember picture] \node[] (pc1) {};!int x = 5;
  !\tikz[remember picture] \node[] (pc2) {};!a();
  !\tikz[remember picture] \node[] (pc3) {};!...
  !\tikz[remember picture] \node[] (pc4) {};!a();
  !\tikz[remember picture] \node[] (pc5) {};!return;   
}
\end{lstlisting}
      \begin{tikzpicture}[remember picture, overlay]
%        \draw<1> node { };
        \draw<2>[decorate,decoration={brace,amplitude=6pt,raise=4pt},yshift=0pt] ($(bt) + (0,0.2)$) -- ($(bb) + (0,-0.2)$) node[xshift=0.2cm] (brace) [midway] {};
        \draw<2> node[right = -0cm of brace, text width = 3cm] {Function \texttt{a} cannot access variable \texttt{x}};

        \draw<3> ($(pc4) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc4);
        \draw<4> ($(a) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (a);
        \draw<5> ($(pc6) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc6);
        \draw<6> ($(pc7) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc7);
        \draw<7-> node[below right = of ret] (w) {\huge ?};
        \draw<7-> (ret) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202},bend left] (w);
        \draw<8> ($(pc5) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc5);
        \draw<9> ($(pc3) + (-0.5,0)$) edge[-stealth,thick,draw={rgb:red,180;green,52;blue,202}] node {} (pc3);
      \end{tikzpicture}
    \end{column}
    \begin{column}{0.5\textwidth}
      \only<2>{Local-state encapsulation}
      \only<3->{Well-bracketed control flow}
    \end{column}
    % What is LSE and WBCF
    % Quick example?
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{Fully-abstract overlay semantics}
  \begin{columns}
\begin{column}{0.5\textwidth}
  \begin{itemize}[<+->]
  \item Compile from oLCM to LCM
  \item Compilation is the identity
  \item Builtin call stack abstraction in oLCM preserved after compilation
  \end{itemize}
\end{column}
\begin{column}{0.5\textwidth}
  \begin{tikzpicture}
    \draw (0,0) node[draw=black, rounded corners] (olcm) {oLCM};
    \draw node[draw=black, rounded corners,below=2.5cm of olcm] (lcm) {LCM};
    \draw (olcm) edge[bend left, ->,thick] (lcm);
    \draw node[left = 3cm of olcm] (ll1) {};
    \draw node[right = 3cm of olcm] (rl1) {};
    \draw node[below = 1.25cm of ll1] (ll) {};
    \draw node[below = 1.25cm of rl1] (rl) {};
    \draw[dashed] (ll) -- (rl);

    \draw<1> (olcm) edge[bend left, ->,thick] node[right, near start] { } (lcm);
    \draw<2-> (olcm) edge[bend left, ->,thick] node[right, near start] {$id$} (lcm);
  \end{tikzpicture}
\end{column}
\end{columns}
\end{frame}

@@

\appendix
\begin{frame}
  \frametitle{Full-abstraction proof sketch}
  \centering
    \begin{tikzpicture}[scale=0.8,every node/.style={scale=.9}]
    % \draw[help lines,yellow] (0,0) grid (10,7);
    \node at (5,4.7) { ${\src{\comp_1}\mathrel{\sconeq} \src{\comp_2}}$ };

    \node at (3.4,4) { ${\plug{\trg{\context}}{\src{\comp_1}} \sterm[]{\gc}{}}$ };
    \node at (5,4) { $\mathrel{\Rightarrow}$ };
    \node at (6.6,4) { ${\plug{\trg{\context}}{\src{\comp_2}} \sterm[]{\gc}{}}$ };

    \node at (4.35,2.8) {  };
    \node at (5,3.6) {  };
    \node at (5.65,2.8) {  };

    \draw[out=100,in=260,double,-implies,double equal sign distance] (4,2.6) to (4,3.4);

    \draw[out=280,in=80,double,-implies,double equal sign distance] (6,3.4) to (6,2.6);

    \node[align=center] at (8.2,3) { $ {\trg{\context}} \cong \trg{\context}$ \\
      $ {\src{\comp_2}} \cong {\src{\comp_2}}$};
    \node[align=center] at (1.8,3) { $ {\trg{\context}} \cong \trg{\context}$ \\
      $ {\src{\comp_1}} \cong {\src{\comp_1}}$};
    % \node at (9,2.7) { $e  {\src{C_1}} \cong \src{C_1}} : tau$ };
    % \node at (8.7,3.3) { $ {\trg{\context}} \cong \trg{\context} :{\emptyset},tau \ra e,{\cdots}$ };
    % \node at (.8,3) { $e  {\src{C_1}} \cong {\src{C_1}} : tau$ };

    \node at (3.4,2) { ${\plug{\trg{\context}}{\src{\comp_1}} \term[]{}}$ };
    \node at (5,2.1) { $\overset{?}{\Rightarrow}$ };
    \node at (6.6,2) { ${\plug{\trg{\context}}{\src{\comp_2}} \term[]{}}$ };

    \node at (5,1.3) { ${\src{\comp_1}}\mathrel{\overset{?}{\tconeq}}{\src{\comp_2}}$ };

    \draw[out=-90,in=90,double,-implies,double equal sign distance] (0,5) to node[sloped, yshift =.7em, below=0.5cm]{\small Contextual equivalence preservation} (0,1);
  \end{tikzpicture}
\end{frame}
